Covariant Phase Space\\[-.2ex]\large\it A Pedagogical Introduction

### 2021-06-24 alpha/CovariantPhaseSpace/charge.tex
Add intro to note on Noether charge

\title{Covariant Phase Space\\\large\it A Pedagogical Introduction}
\addbibresource{charge.bib}

@@

\addtocounter{section}{-1}
\section{Conventions}
	We follow Prof.~Wei Song's lecture notes on $\mrm{AdS}_3/\mrm{CFT}_2$, which include a very nice introduction to the covariant formalism and its application. 
	When it comes to notations, we try to follow the conventions of \textcite{Harlow:2019yfa}, with the following exceptions and extensions:

@@

@@

	\item Hodge dual of a $p$-form $\omega$ is defined as contraction with the volume form:
	\begin{equation}
		\hstar\omega
		= \frac{1}{p!}\,
			\omega^\sharp \cdot \mrm{Vol}_M
	\quad\Longleftrightarrow\quad
		\eta\wedge \hstar\omega
		= \aqty{\eta,\omega} \,\mrm{Vol}_M
	\end{equation}
	$\aqty{\cdot,\cdot}$ is the induced inner product on the space of $p$-forms. 
	The $\frac{1}{p!}$ factor is necessary to guarentee that $\hstar\hstar\omega = (-1)^s\cdot(-1)^{p(D-p)} \omega$. Again the $(-1)^s$ comes from signature of the metric. In particular, for a scalar $f$ and a vector $V$, we have:
	\begin{equation}
		\hstar f
		= f\sqrt{\abs{g}} \dd[D]{x},
	\quad
		\hstar\,(f\sqrt{\abs{g}} \dd[D]{x})
		= (-1)^s f,
	\quad
		\hstar V^\flat
		= V\cdot \sqrt{\abs{g}} \dd[D]{x}
	\end{equation}
	A particular useful relation is:
	\begin{equation}
		\dd{\hstar V^\flat}
		= \hstar\,(\cdv{\mu} V^\mu)
	\end{equation}
	This is derived around \eqref{eq:divergence_form}. The inner product $\aqty{\cdot,\cdot}$ is particularly convenient for 1-forms; in this case we have:
	\begin{equation}
		n \wedge\hstar j^\flat
		= n_\mu j^\mu \,\mrm{Vol}_M
	\end{equation}

>>>>

\title{Covariant Phase Space\\[-.2ex]\large\it A Pedagogical Introduction}
\addbibresource{charge.bib}

@@

\addtocounter{section}{-1}
\section{Introduction \& Conventions}
	The phase space is understood as the space of \textit{all solutions} of the equations of motion (EoMs), satisfying the boundary conditions; alternatively, we can think of it as a collection of all possible \textit{initial configurations} of the system, and the additional \textit{symplectic structure} specifies their evolutions. This idea is best explained by \textcite{Crnkovic:1986ex}.

	The inspiration comes from the Lagrangian treatment of field theory, where we work with:
	\begin{equation}
		\pi^\mu = \pdv{\mcal{L}}{(\pd_\mu\phi)}
	\end{equation}
	Which preserves general covariance. But $(\pi_\mu,\phi)$ is not a set of independent coordinates; they are constrained by the equations of motion (EoMs). The rough idea is that we start with $(\pi_\mu,\phi)$, and then reduce it to the independent variables $(\pi,\phi)$ by imposing the EoMs, and possibly, additional constraints due to gauge redundancy.

	In this note we review the covariant formalism in a systematic yet pedagogical manner. 
	We follow Prof.~Wei Song's lecture notes on $\mrm{AdS}_3/\mrm{CFT}_2$, which include a very nice introduction to the covariant formalism and its application. 
	When it comes to notations, we try to follow the conventions of \textcite{Harlow:2019yfa}, with the following exceptions and extensions:

@@

	For simplicity, sometimes we might omit the explicit notations of musical isomorphisms, but they are nonetheless implied; e.g.~the normal (co-)vector $n$ can be understood as $n^\mu$ or $n_\mu$.

@@

	\item Hodge dual of a $p$-form $\omega$ is defined as contraction with the volume form:
	\begin{equation}
		\hstar\omega
		= \frac{1}{p!}\,
			\omega^\sharp \cdot \mrm{Vol}_M
	\quad\Longleftrightarrow\quad
		\eta\wedge \hstar\omega
		= \aqty{\eta,\omega} \,\mrm{Vol}_M
	\end{equation}
	$\aqty{\cdot,\cdot}$ is the induced inner product on the space of $p$-forms. 
	The $\frac{1}{p!}$ factor is necessary to guarentee that $\hstar\hstar\omega = (-1)^s\cdot(-1)^{p(D-p)} \omega$. Again the $(-1)^s$ comes from signature of the metric. In particular, for a scalar $f$ and a vector $V$, we have:
	\begin{equation}
		\hstar f
		= f\sqrt{\abs{g}} \dd[D]{x},
	\quad
		\hstar\,(f\sqrt{\abs{g}} \dd[D]{x})
		= (-1)^s f,
	\quad
		\hstar \theta^\flat
		= \theta\cdot \sqrt{\abs{g}} \dd[D]{x}
	\end{equation}
	It's convenient to only act $\hstar$ on the form of a smaller degree to get the form of a larger degree; in this way we don't need to worry about the $(-1)^s$ factor. 
	A particular useful relation is:
	\begin{equation}
		\dd{\hstar \theta^\flat}
		= \hstar\,(\cdv{\mu} \theta^\mu)
	\end{equation}
	This is derived around \eqref{eq:divergence_form}. The inner product $\aqty{\cdot,\cdot}$ is particularly convenient for 1-forms; in this case we have:
	\begin{equation}
		n \wedge\hstar j^\flat
		= n_\mu j^\mu \,\mrm{Vol}_M
	\end{equation}
